% ------------------------
% Resume
% Author : Dipesh Maindolia
% ------------------------

\documentclass[letterpaper,8.5pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{fontenc}
\usepackage{lmodern}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}

\pagestyle{empty}

% ---------- MARGINS ----------
\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\evensidemargin}{-0.65in}
\addtolength{\textwidth}{1.30in}
\addtolength{\topmargin}{-0.95in}
\addtolength{\textheight}{2.40in}

\urlstyle{same}
\raggedright
\linespread{0.85}

\setlength{\tabcolsep}{0in}
\setlength{\parskip}{0pt}

\definecolor{linkblue}{RGB}{26, 86, 160}

% ---------- LINK ICON ----------
\newcommand{\linkicon}[1]{\href{#1}{\raisebox{-0.1em}{%
\begin{tikzpicture}[baseline, x=0.4pt, y=0.4pt, line width=2.6, line cap=round, line join=round, color=linkblue]
  \draw (4,4) -- (4,20) -- (13,20);
  \draw (4,4) -- (20,4) -- (20,13);
  \draw[-{Latex[length=3pt,width=2.6pt]}] (9,11) -- (24,26);
\end{tikzpicture}%
}}}

\setlist[itemize]{
  leftmargin=0.18in,
  noitemsep,
  topsep=0.5pt,
  parsep=0pt,
  partopsep=0pt
}

% ---------- SECTION STYLE ----------
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\normalsize\bfseries
}{}{0em}{}[\titlerule \vspace{0.5pt}]

% ---------- CUSTOM COMMANDS ----------
\newcommand{\resumeSubheading}[4]{
  \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \textbf{#1} & \small\textit{#2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
}

\newcommand{\resumeProject}[2]{
  \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \textbf{#1} & \textit{\small #2} \\
  \end{tabular*}
}

% ---------- DOCUMENT ----------
\begin{document}

% ---------- HEADER ----------
\begin{center}
    {\LARGE \textbf{Dipesh Maindolia}} \\[2pt]
    {\small
    Ramnagar, Uttarakhand, India \textbar\
    +91 7017982390 \textbar\
    \href{mailto:dipeshmaindolia000@gmail.com}{\color{linkblue}dipeshmaindolia000@gmail.com}
    \textbar\
    \href{https://linkedin.com/in/dipeshmaindolia}{\color{linkblue}LinkedIn}
    \textbar\
    \href{https://github.com/dipeshmaindolia001}{\color{linkblue}GitHub}
    }
\end{center}

\vspace{-6pt}

% ---------- EDUCATION ----------
\section{Education}

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} c r}
\textbf{B.S. in Data Science and Applications} & \textbf{CGPA: 6.85} & \textbf{2023 -- Present} \\
\textit{Indian Institute of Technology Madras} & & \\[0.5pt]

\textbf{B.Tech in Information Technology} & \textbf{CGPA: 7.4} & \textbf{2022 -- 2026} \\
\textit{College of Technology, Pantnagar} & & \\[0.5pt]

\textbf{Senior Secondary (Class XII)} & \textbf{92\%} & \textbf{2021} \\
\textit{St. Joseph Convent School} & & \\[0.5pt]

\textbf{High School (Class X)} & \textbf{92\%} & \textbf{2019} \\
\textit{USR Indu Inter College} & & \\
\end{tabular*}

\vspace{-6pt}

% ---------- EXPERIENCE ----------
\section{Experience}

\resumeSubheading{Interviewkit.ai}{(Remote)}{Product Analyst Intern}{April 2026 -- June 2026}
\begin{itemize}
    \item \textbf{Product \& Feature Development:} Collaborated directly with the founder on product strategy, feature planning, and execution while improving platform workflows and user engagement systems.
    \item \textbf{REST API \& Recommendation Module:} Built a REST API editor and an intelligent job recommendation module using keyword extraction, structured filtering, and profile-matching techniques.
    \item \textbf{Interview Q\&A System:} Developed a resume-based system capable of auto-generating personalized technical interview questions and detailed model answers.
\end{itemize}

\vspace{1pt}

\textbf{CrackNonTech} \hfill May 2026 -- June 2026 \\
\textit{Analyst Fellowship}

\begin{itemize}
    \item \textbf{Business Strategy:} Studied \textbf{profitability analysis}, \textbf{market entry frameworks} and
    \textbf{cost-benefit evaluation} through case studies, mentor-led sessions, industry scenarios and group problem-solving.

    \item \textbf{Analytical Tools:} Sharpened \textbf{SQL querying}, \textbf{Python scripting} and \textbf{guesstimate}
    skills to model business problems, estimate market sizes and present structured data-driven strategic recommendations.
\end{itemize}

\vspace{-5pt}

% ---------- PROJECTS ----------
\section{Projects}

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
\textbf{YouTube Trending Data Pipeline on AWS} & \href{https://github.com/dipeshmaindolia001/YouTube-Trending-Data-Pipeline-on-AWS}{\small\color{linkblue}GitHub} \\
\end{tabular*}
\begin{itemize}
    \item \textbf{Pipeline Design:} Built a fully \textbf{automated end-to-end data pipeline} using \textbf{AWS S3,
    Lambda and Glue} with the \textbf{YouTube Data API} to continuously ingest, clean, transform, partition and store data.
    \item \textbf{Architecture \& Orchestration:} Implemented \textbf{Medallion Architecture} with \textbf{Bronze, Silver
    and Gold layers} and \textbf{AWS Step Functions} for reliable orchestration, scheduling, retry logic, alerts and monitoring.
\end{itemize}

\vspace{0.5pt}

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
\textbf{Flight Price Prediction using AWS SageMaker} & \href{https://github.com/dipeshmaindolia001/sagemaker-flight-prices-prediction}{\small\color{linkblue}GitHub} \\
\end{tabular*}
\begin{itemize}
    \item \textbf{End-to-End ML Pipeline:} Built a complete flight price prediction system on \textbf{AWS SageMaker}, covering data preprocessing, feature engineering, model training and hyperparameter tuning using \textbf{XGBoost} with \textbf{Bayesian optimization} via SageMaker's \textbf{HyperparameterTuner}.
    \item \textbf{Feature Engineering \& Deployment:} Engineered features from raw flight data (airline, route, timestamps, duration) using advanced \textbf{scikit-learn Pipelines, FeatureUnion} and custom transformers; deployed a \textbf{Streamlit} web application to \textbf{Streamlit Cloud} for real-time price predictions.
\end{itemize}

\vspace{0.5pt}

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
\textbf{Ola Data Analytics End-to-End Project} & \href{https://github.com/dipeshmaindolia001/Ola-Data-Analytics-End-to-End-Project}{\small\color{linkblue}GitHub} \\
\end{tabular*}
\begin{itemize}
    \item \textbf{Data Analysis:} Analyzed \textbf{ride booking datasets} using \textbf{SQL}, \textbf{Excel} and
    \textbf{Power BI} to surface insights on ride demand, peak hours, revenue, driver ratings, vehicle types and cancellations.
    \item \textbf{Dashboard \& Reporting:} Built \textbf{interactive Power BI dashboards} with \textbf{KPI cards, slicers,
    drill-throughs and trend charts} to monitor operations and enable data-backed decisions across all business functions.
\end{itemize}

\vspace{-5pt}

% ---------- SKILLS ----------
\section{Technical Skills}

\begin{tabular*}{\textwidth}{l @{\hspace{1.5em}} l @{\hspace{1.5em}} l @{\hspace{1.5em}} l}
\textbullet\ \textbf{Languages:} C++, Python, SQL &
\textbullet\ \textbf{BI \& Analytics:} Excel, Power BI &
\textbullet\ \textbf{Cloud:} AWS &
\textbullet\ \textbf{ML:} Machine Learning \\
\end{tabular*}

\vspace{-5pt}

% ---------- POSITION OF RESPONSIBILITY ----------
\section{Position of Responsibility}

\textbf{Convocation Digital Card Team Lead}
\begin{itemize}
    \item \textbf{Team Leadership:} Led the end-to-end \textbf{digital invitation and QR-based security verification
    system} for the university convocation, coordinating a cross-functional team across design, dev and operations.
    \item \textbf{Cost Impact:} Eliminated paper-based manual workflows and contributed to \textbf{Rs.~1.5 lakh in
    cost savings} by deploying a scalable digital check-in system with real-time entry validation and audit logs.
\end{itemize}

\vspace{-5pt}

% ---------- ACHIEVEMENTS ----------
\section{Achievements}

\begin{itemize}
    \item \textbf{GATE:} Cleared \textbf{GATE CSE 2026} and \textbf{GATE DA 2025} with \textbf{94.3 percentile} and
    \textbf{86 percentile} respectively, qualifying among the top rankers in highly competitive national-level exams.
    \item \textbf{EdTech Initiative -- Pantnagar Pathshala:} Built and scaled
    \href{https://pantnagar-pathshala.vercel.app/}{\underline{\color{linkblue}\textbf{Pantnagar Pathshala}}}\linkicon{https://pantnagar-pathshala.vercel.app/}, an EdTech
    platform for Pantnagar entrance exam preparation, alongside an associated
    \href{https://www.youtube.com/@dipeshmaindolia}{\underline{\color{linkblue}\textbf{YouTube channel}}}\linkicon{https://www.youtube.com/@dipeshmaindolia} that crossed
    \textbf{1,000+ subscribers}.
    \item \textbf{Academic \& Creative:} Secured \textbf{2nd Position} in the Shutterbug Short Film Competition and
    achieved \textbf{100/100 in Mathematics} in Class X Boards, showcasing both analytical and creative strengths.
    \item \textbf{Freelance Creative Work:} Independently delivered \textbf{video editing} and \textbf{thumbnail design}
    for multiple YouTube creators and branding clients, producing high-quality content that grew channel engagement.
\end{itemize}

\end{document}